Temporal stability in human interaction networks: sector sizes, topological prominence and time activity

### 2015-10-06 paper.tex
arrumada tabela com os quantis

\begin{table}[h]
	\caption{Distribution of activity among participants.
The first column presents the percentage of messages sent by the most active participant.
The column for the first quartile ($1Q$) exposes 
the minimum percentage of participants
responsible for at least 25\% of total messages with the actual number in parenthesis.
Similarly, the column for the first three quartiles $3Q$
gives the minimum percentage of participants responsible for 75\% of total messages.
The last decile $-10D$ column exposes the maximum percentage of participants responsible for 10\% of messages.}
	\begin{center}
		\begin{tabular}{ | l ||  c | c | c | c | }
			\hline
			list & hub & $ 1Q $ & $ 3Q $ & $-10D$ \\ \hline
			\input{tables/userTab}
		\end{tabular}
	\end{center}
	\label{autores}
\end{table}

>>>>

\begin{table}[h]
	\caption{Distribution of activity among participants.
The first column presents the percentage of messages sent by the most active participant.
The column for the first quartile ($Q_1$) exposes 
the minimum percentage of participants
responsible for at least 25\% of total messages with the actual number in parenthesis.
Similarly, the column for the first three quartiles $Q_3$
gives the minimum percentage of participants responsible for 75\% of total messages.
The last decile $D_{-1}$ column exposes the maximum percentage of participants responsible for 10\% of messages.}
	\begin{center}
		\begin{tabular}{ | l ||  c | c | c | c | }
			\hline
			list & hub & $ Q_1 $ & $ Q_3 $ & $D_{-1}$ \\ \hline
			\input{tables/userTab}
		\end{tabular}
	\end{center}
	\label{autores}
\end{table}
